---
title: "Capstone Analysis"
author: "Yusei Hara"
date: "2020/11/11"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ASER Pakistan 2016

<p>In this piece of paper, a set of data obtained from Annual Status of Education Report (ASER) is explored. The raw data was downloaded from the link here. https://palnetwork.org/aser-centre/</p>

### Preparation
#### Packages Used
```{r libraries, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(ggrepel)
library(gghighlight)
library(stringr)
library(dplyr)
library(sf)
library(scatterplot3d)
library(car)
library(ResourceSelection) #to excute Hosmer-Lemeshow test
# library(broom)
require(ggiraph)
require(ggiraphExtra)
# require(plyr)
```

### Data Installation

#### ASER2016

```{r}
provdist <- read.csv("aser/ASER2016ProvDist.csv")
school <- read.csv("aser/ASER2016GSchool.csv")
child <- read.csv("aser/ASER2016Child.csv")
pschool <- read.csv("aser/ASER2016PvtSchool.csv")
gschool <- read.csv("aser/ASER2016GSchool.csv")
parent <- read.csv("aser/ASER2016Parent.csv")
house <- read.csv("aser/ASER2016HouseholdIndicators.csv")
```

```{r}
RegionName <- c("2" = "Panjab", 
                "3" = "Sindh", 
                "4" = "Balochistan", 
                "5" = "Khyber Pakhtunkhwa", 
                "6" = "Gilgit-Baltistan", 
                "7" = "Azad Jammu and Kashmir", 
                "8" = "Islamabad - ICT", 
                "9" = "Federally Administrated Tribal Areas")
Gender <- c("0" = "Male",
            "-1" = "Female")
```

#### Spatial Data

```{r}
ica <- sf::st_read("map/pak_ica_categories_areas_geonode_apr2017.shp")
```

### Data Wrangling

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica %>% 
  mutate(
    centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(aes(x, y))
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(aes(x, y)) +
  geom_text(aes(x, y, label = Districts),size = 2, check_overlap = TRUE, nudge_y = 1)
```

```{r}
ica_df <- ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
  as.data.frame()

ica_df <- ica_df %>% select(Province, Districts, x, y)
ica_df <- ica_df %>% summarize(Province = tolower(Province), Districts = tolower(Districts), x = x, y = y)
```

#### Child and ProvDist data combination

```{r}
child_dname <- child %>% left_join(provdist[-1])
child_dname <- child_dname %>% mutate(dname = tolower(DNAME))
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_2 <- ica_df %>% filter(Province == "punjab")
ica_df_2$Districts <- ica_df_2$Districts %>%  
  str_replace("bahawalnagar", "bahawalnager") %>%
  str_replace("jhelum", "Jehlum") %>% 
  str_replace("leiah", "layyah") %>% 
  str_replace("mandi bahauddin", "mandi bahuddin") %>% 
  as.vector()


child_dname_2 <- child_dname %>% filter(RNAME == "Punjab") %>% left_join(ica_df_2, by = c("dname" = "Districts"))

child_dname_2 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_2
```

```{r}
ica_df_3 <- ica_df %>% filter(Province == "sindh")

ica_df_3$Districts <- ica_df_3$Districts %>%  
  str_replace("ghotki", "gotki") %>%
  str_replace("mirpur khas", "mirpurkhas") %>% 
  str_replace("malir karachi", "karachi-malir-rural") %>% 
  str_replace("naushahro feroze", "nowshero feroze") %>% 
  str_replace("kambar shahdad kot", "qambar shahdadkot") %>% 
  str_replace("sujawal", "sajawal") %>% 
  str_replace("shaheed benazir abad", "shaheed benazirabad") %>% 
  str_replace("tando allahyar", "tando allah yar") %>% 
  as.vector()

child_dname_3 <- child_dname %>% filter(RNAME == "Sindh") %>% left_join(ica_df_3, by = c("dname" = "Districts"))

child_dname_3 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_3
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_4 <- ica_df %>% filter(Province == "balochistan")

ica_df_4$Districts <- ica_df_4$Districts %>%  
  str_replace("chagai", "chaghi") %>%
  str_replace("jaffarabad", "jafarabad") %>% 
  str_replace("kalat", "kallat") %>% 
  str_replace("kech", "kech (turbat)") %>% 
  str_replace("killa abdullah", "qilla abdullah") %>% 
  str_replace("killa saifullah", "qilla saifullah") %>% 
  as.vector()

child_dname_4 <- child_dname %>% filter(RNAME == "Balochistan") %>% left_join(ica_df_4, by = c("dname" = "Districts"))

child_dname_4 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_4
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_5 <- ica_df %>% filter(Province == "khyber pakhtunkhwa")
ica_df_5

ica_df_5$Districts <- ica_df_5$Districts %>%  
  str_replace("batagram", "battagram") %>%
  str_replace("d. i. khan", "dera ismail khan") %>% 
  str_replace("malakand p area", "malakand") %>% 
  as.vector()

child_dname_5 <- child_dname %>% filter(RNAME == "Khyber Pakhtunkhwa") %>% left_join(ica_df_5, by = c("dname" = "Districts"))

child_dname_5 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_5
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_6 <- ica_df %>% filter(Province == "gilgit baltistan")

ica_df_6$Districts <- ica_df_6$Districts %>%  
  str_replace("diamir", "diamer") %>%
  str_replace("hunza", "hunza-nagar") %>% 
  as.vector()

child_dname_6 <- child_dname %>% filter(RNAME == "Gilgit-Baltistan") %>% left_join(ica_df_6, by = c("dname" = "Districts"))

child_dname_6 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_6
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_7 <- ica_df %>% filter(Province == "azad kashmir")

ica_df_7$Districts <- ica_df_7$Districts %>%  
  str_replace("hattian bala", "hattian") %>%
  str_replace("haveli\\(kahuta\\)", "haveli") %>% 
  str_replace("sudhnoti", "sudhnati") %>% 
  as.vector()

child_dname_7 <- child_dname %>% filter(RNAME == "Azad Jammu and Kashmir") %>% left_join(ica_df_7, by = c("dname" = "Districts"))

child_dname_7 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_7
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_8 <- ica_df %>% filter(Province == "islamabad")
child_dname_8 <- child_dname %>% filter(RNAME == "Islamabad - ICT") %>% left_join(ica_df_8, by = c("dname" = "Districts"))

child_dname_8 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_8
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_9 <- ica_df %>% filter(Province == "fata")

ica_df_9$Districts <- ica_df_9$Districts %>%  
  str_replace("fr bannu", "f.r. - bannu") %>%
  str_replace("fr d.i.khan", "f.r. - d.i. khan") %>% 
  str_replace("fr kohat", "f.r. - kohat") %>% 
  str_replace("fr lakki marwat", "f.r. - lakki marwat") %>% 
  str_replace("fr peshawar", "f.r. - peshawar") %>% 
  str_replace("fr tank", "f.r. - tank") %>% 
  as.vector()

child_dname_9 <- child_dname %>% filter(RNAME == "Federally Administrated Tribal Areas") %>% left_join(ica_df_9, by = c("dname" = "Districts"))

child_dname_9 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_9
```

```{r ica_df whose Districts names are renamed,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df
rbind(ica_df_2, ica_df_3, ica_df_4,
      ica_df_5, ica_df_6, ica_df_7,
      ica_df_8, ica_df_9)
```

```{r data child which as location,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
child_ica <- rbind(child_dname_2, child_dname_3, child_dname_4,
      child_dname_5, child_dname_6, child_dname_7,
      child_dname_8, child_dname_9)
```


### Preparation for Logistic Regression Analysis

#### Making Dataframe With Dummy Variables

```{r}
child_ica_dummy <- child_ica %>% filter(!is.na(C002), !is.na(C003), !is.na(PR004), !is.na(PR009))
child_ica_dummy$C002_01 <- ifelse(child_ica_dummy$C002 == -1, 1, 0)
child_ica_dummy$C003_01 <- ifelse(child_ica_dummy$C003 == 3, 1, 0)     # currently-enrolled
child_ica_dummy$C003_1_01 <- ifelse(child_ica_dummy$C003 == 1, 1, 0)   # never-enrolled
child_ica_dummy$C003_2_01 <- ifelse(child_ica_dummy$C003 == 2, 1, 0)   # drop-out
child_ica_dummy$PR004_01 <- ifelse(child_ica_dummy$PR004 == -1, 1, 0)
child_ica_dummy$PR009_01 <- ifelse(child_ica_dummy$PR009 == -1, 1, 0)
child_ica_dummy$PR004_PR009_01 <- ifelse(
  child_ica_dummy$PR004 == -1 | child_ica_dummy$PR009 == -1, 1, 0)


child_ica_dummy$PR004_only_01 <- ifelse(
  child_ica_dummy$PR004 == -1 & child_ica_dummy$PR009 == 0, 1, 0)
child_ica_dummy$PR009_only_01 <- ifelse(
  child_ica_dummy$PR004 == 0 & child_ica_dummy$PR009 == -1, 1, 0)
child_ica_dummy$PR004_PR009_both_01 <- ifelse(
  child_ica_dummy$PR004 == -1 & child_ica_dummy$PR009 == -1, 1, 0)
```

```{r}
n_children_in_household <- child_ica_dummy %>% 
  group_by(HHID) %>% 
  summarize(n_children_in_household = length(unique(CID)))

child_ica_dummy <- child_ica_dummy %>% left_join(n_children_in_household)

child_ica_dummy$H002_1_01 <- ifelse(child_ica_dummy$H002 == 1, 1, 0)
child_ica_dummy$H002_2_01 <- ifelse(child_ica_dummy$H002 == 2, 1, 0)
child_ica_dummy$H002_3_01 <- ifelse(child_ica_dummy$H002 == 3, 1, 0)
```

#### Regional Dummy Variables

```{r}
child_ica_dummy <- child_ica_dummy
child_ica_dummy$Panjab <- ifelse(child_ica_dummy$RID == 2, 1, 0)
child_ica_dummy$Sindh <- ifelse(child_ica_dummy$RID == 3, 1, 0)
child_ica_dummy$Balochistan <- ifelse(child_ica_dummy$RID == 4, 1, 0)
child_ica_dummy$Khyber_Pakhtunkhwa <- ifelse(child_ica_dummy$RID == 5, 1, 0)
child_ica_dummy$Gilgit_Baltistan <- ifelse(child_ica_dummy$RID == 6, 1, 0)
child_ica_dummy$Azad_Jammu_and_Kashmir <- ifelse(child_ica_dummy$RID == 7, 1, 0)
child_ica_dummy$Islamabad_ICT <- ifelse(child_ica_dummy$RID == 8, 1, 0)
child_ica_dummy$Federally_Administrated_Tribal_Areas <- ifelse(child_ica_dummy$RID == 9, 1, 0)
```

```{r}
dists_near_hunza_1 <- c(178, 199, 243, 259, 265, 266, 267, 270, 273, 274)
child_ica_dummy$DID_near_hunza_1 <- ifelse(child_ica_dummy$DID %in% dists_near_hunza_1, 1, 0)
dists_near_hunza_2 <- c(176, 178, 185, 199, 243, 245, 259, 265, 267, 270, 273, 274)
child_ica_dummy$DID_near_hunza_2 <- ifelse(child_ica_dummy$DID %in% dists_near_hunza_2, 1, 0)
```

#### Factor Variables

```{r}
child_ica_dummy$DID <- child_ica_dummy$DID %>% as.factor()
```



### Notes on Data Wrangling

#### Eliminated NAs

```{r}
child_ica %>% 
  summarize(C002_na = sum(is.na(C002)),
            C003_na = sum(is.na(C003)),
            PR004_na = sum(is.na(PR004)),
            PR009_na = sum(is.na(PR009)))
```

#### Eliminated Rows in Total

```{r}
data.frame(original_rows = nrow(child_ica),
           eliminated_rows = nrow(child_ica) - nrow(child_ica_dummy),
           ratio = (nrow(child_ica)-nrow(child_ica_dummy))/nrow(child_ica))

```

#### Eliminated NAs Hunza

```{r}
child_ica %>% 
  filter(DID == 266) %>% 
  summarize(C002_na = sum(is.na(C002)),
            C003_na = sum(is.na(C003)),
            PR004_na = sum(is.na(PR004)),
            PR009_na = sum(is.na(PR009)))
```

#### Eliminated Rows in Total Hunza

```{r}
data.frame(original_rows = nrow(child_ica %>% filter(DID == 266)),
           eliminated_rows = nrow(child_ica %>% filter(DID == 266)) - nrow(child_ica_dummy %>% filter(DID == 266)),
           ratio = (nrow(child_ica %>% filter(DID == 266) %>% filter(DID == 266))-nrow(child_ica_dummy %>% filter(DID == 266)))/nrow(child_ica %>% filter(DID == 266)))

```



### Generalized Linear Models

#### Hunza. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01, family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5, DID == 266))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### AIC

```{r}
extractAIC(glm_child)
```

##### BIC

```{r}
extractAIC(glm_child, k = log(nrow(glm_child$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5, DID == 266))
anova(glm_child_null, glm_child, test = "Chisq")
```

##### variables selection

```{r}
step(glm_child_null, direction = "both", 
     scope = (~ C001 + C002_01 + PR004_PR009_both_01 + n_children_in_household))
```

##### multicolinearity

```{r}
vif(glm_child)

```


#### Whole Pak. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01 + relevel(DID, ref = "266")

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01 + relevel(DID, ref = "266"), family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5))

glm_child %>% summary()
```

```{r}
glm_child %>% 
  summary() %>% 
  .$coefficient %>% 
  as.data.frame() %>% 
  select(`Pr(>|z|)`) %>% 
  filter(`Pr(>|z|)` > 0.05) %>% 
  row.names() %>% 
  str_split("\\)") %>% 
  as.data.frame() %>% 
  gather() %>% 
  select(value) %>% 
  .[seq(2,24,2),] %>% 
  as.numeric()
```


#### dists_near_hunza_2. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01, family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5, DID %in% dists_near_hunza_2))

glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```


#### dists_near_hunza_2 or Not. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01 + DID_near_hunza_2

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01 + DID_near_hunza_2, family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5))

glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```



#### Not dists_near_hunza. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01 + as.factor(H004)

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + C002_01 + PR004_PR009_both_01 + as.factor(H004), family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5, !DID %in% dists_near_hunza_2))

glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### multicolinearity

```{r}
vif(glm_child)
```

```{r}
g_n <- gschool %>% 
  group_by(DID) %>% 
  summarize(g_n = sum(unique(GSID)))
```
```{r}
p_n <- pschool %>% 
  group_by(DID) %>% 
  summarize(p_n = sum(unique(PSID)))
```

```{r}
school_type <- g_n %>% full_join(p_n) %>% 
  mutate(ratio = p_n/(g_n + p_n))
school_type$DID <- as.factor(school_type$DID)
```

```{r}
child_ica_dummy %>% 
  full_join(school_type)
```

#### Not dists_near_hunza. GLM Age >= 5 ratio + C002_01 + PR004_PR009_both_01

```{r}
glm_child <- glm(C003_01 ~ ratio + C002_01 + PR004_PR009_both_01, family = "binomial", data = child_ica_dummy %>% full_join(school_type) %>% filter(C001 >= 5, !DID %in% dists_near_hunza_2))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
# glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

#### Not dists_near_hunza. GLM Age >= 5 n_children_in_household + ratio + C002_01 + PR004_PR009_both_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + ratio + C002_01 + PR004_PR009_both_01, family = "binomial", data = child_ica_dummy %>% full_join(school_type) %>% filter(C001 >= 5, !DID %in% dists_near_hunza_2))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
# glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child)) 
```





#### Each Dist. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01

```{r}
each_dist <- sapply(as.numeric(as.character(unique(child_ica_dummy$DID))), function(id){
  child_ica_dummy <- child_ica_dummy %>% filter(DID == id)
  glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01, 
                   family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5))
  temp_hoslem <- hoslem.test(x = glm_child$y, y = fitted(glm_child))
  data.frame(DID = id, hoslem_p_value = temp_hoslem$p.value)
}) %>% t()
each_dist
```

```{r}
each_dist <- each_dist %>% 
  as.data.frame() 
each_dist$DID <- each_dist %>% 
  pull(DID) %>% 
  as.numeric()
each_dist$hoslem_p_value <- each_dist %>% 
  pull(hoslem_p_value) %>% 
  as.numeric()
each_dist
```

#### Dists with P value <= 0.05

```{r}
each_dist %>% 
  filter(hoslem_p_value <= 0.05)
```

```{r}
dists_not_fit <- each_dist %>% 
  filter(hoslem_p_value <= 0.05) %>% 
  pull(DID)
```


#### Not dists_not_fit. GLM Age >= 5 C003_01 ~ n_children_in_household + PR004_PR009_both_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_both_01, family = "binomial", data = child_ica_dummy %>% filter(C001 >= 5, !DID %in% dists_not_fit))

glm_child %>% summary()
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```




<!-- ### memo -->

<!-- #### fit the model -->

<!-- ```{r} -->
<!-- glm_child <- glm(C003_01~ C001 + C002_01 + PR004_01, family = "binomial", data = child_ica_dummy) -->

<!-- summary(glm_child) -->
<!-- ``` -->

<!-- ##### exponential transformation -->

<!-- ```{r} -->
<!-- exp(glm_child$coefficients) -->
<!-- ``` -->

<!-- ##### confidence interval (intercept and coefficient) -->

<!-- ```{r} -->
<!-- confint(glm_child, level = 0.95) -->
<!-- ``` -->

<!-- ##### exponential transformation of confidence interval (odds ratio of intercept and coefficient) -->

<!-- ```{r} -->
<!-- exp(confint(glm_child, level = 0.95)) -->
<!-- ``` -->

<!-- ##### AIC -->

<!-- ```{r} -->
<!-- extractAIC(glm_child) -->
<!-- ``` -->

<!-- ##### BIC -->

<!-- ```{r} -->
<!-- extractAIC(glm_child, k = log(nrow(glm_child$data))) -->
<!-- ``` -->

<!-- ##### effectiveness of explanatory variables -->

<!-- ```{r} -->
<!-- glm_child_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy) -->
<!-- anova(glm_child_null, glm_child, test = "Chisq") -->
<!-- ``` -->

<!-- ##### variables selection -->

<!-- ```{r} -->
<!-- step(glm_child_null, direction = "both",  -->
<!--      scope = (~ C001 + C002_01 + PR004_01 + PR009_01)) -->
<!-- ``` -->

<!-- ##### multicolinearity -->

<!-- ```{r} -->
<!-- vif(glm_child) -->

<!-- ``` -->


