---
title: "Exploring ASER2016 Pakistan Data"
author: "Yusei Hara"
date: "2020/10/1"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ASER Pakistan 2016

<p>In this piece of paper, a set of data obtained from Annual Status of Education Report (ASER) is explored. The raw data was downloaded from the link here. https://palnetwork.org/aser-centre/</p>

### Preparation
#### Packages Used
```{r libraries, message=FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(ggrepel)
library(gghighlight)
library(stringr)
library(dplyr)
library(sf)
library(scatterplot3d)
library(car)
library(ResourceSelection) #to excute Hosmer-Lemeshow test
# library(broom)
require(ggiraph)
require(ggiraphExtra)
# require(plyr)
```
#### Data Installation
```{r}
provdist <- read.csv("aser/ASER2016ProvDist.csv")
school <- read.csv("aser/ASER2016GSchool.csv")
child <- read.csv("aser/ASER2016Child.csv")
pschool <- read.csv("aser/ASER2016PvtSchool.csv")
gschool <- read.csv("aser/ASER2016GSchool.csv")
parent <- read.csv("aser/ASER2016Parent.csv")
house <- read.csv("aser/ASER2016HouseholdIndicators.csv")
```
```{r}
RegionName <- c("2" = "Panjab", 
                "3" = "Sindh", 
                "4" = "Balochistan", 
                "5" = "Khyber Pakhtunkhwa", 
                "6" = "Gilgit-Baltistan", 
                "7" = "Azad Jammu and Kashmir", 
                "8" = "Islamabad - ICT", 
                "9" = "Federally Administrated Tribal Areas")
Gender <- c("0" = "Male",
            "-1" = "Female")
```


### Exploration
#### Checking Samplesizes
```{r}
length(unique(child$CID))
```
<p>The whole samplesize (the numebr of children) of this dataset is 255196.</p>
```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(N_hunza = length(unique(CID)))
```
<p>The samplesize of Hunza alone is 1641.</p>









### Exploration in Hunza
#### Gender Proportion
```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(gender_proportion = mean(C002))
```
<p>-1: female, 0: male<br>
gender_proportion = -0.5173675 means there are a little more girls in the dataset.</p>

#### Age of Children (C001)
```{r, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C001)) +
  geom_histogram()
```
<p>Age is well sparsed</p>

#### Eduation Status

```{r}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C003)) +
  geom_histogram(bins = 3)
```
<p>1 = never enrolled; 2 = drop-out; 3 = currently enrolled</p>

#### Education Status by Gender
```{r}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C003)) +
  geom_histogram(bins = 3, binwidth = 1) +
  facet_grid(~C002, labeller = labeller(C002 = Gender))
```
<p>Both genders look pretty good interms of the absolute number of currently-enrolled-children </p>

#### The Enrollment Rate by Gender
```{r, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  group_by(C002) %>% 
  mutate(enrollment_rate = mean(C003 == 3)) %>% 
  ggplot(aes(C002, enrollment_rate)) +
  geom_col() +
  scale_y_continuous() +
  geom_label(aes(label = enrollment_rate)) +
  scale_x_continuous(breaks = c(-1, 0), labels = c("Female", "Male"))
```
<p>As a rate, both are doing pretty good</p>

#### Currently-Enrolled: Institution Type (C006) in Hunza
1 = Government; 2 = Private; 3 = Madrasah(Conventional religious education) School; 4 = Other(Non formal education facility)
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C006)) +
  geom_histogram()
```

<p>Most children go to public schools or private schools</p>


#### Within Gilgit-Baltistan 
```{r}
child %>% 
  filter(RID == 6) %>% 
  group_by(DID) %>% 
  mutate(Current_Enrollment_Rate = mean(C003 == 3)) %>% 
  ggplot(aes(DID, Current_Enrollment_Rate)) +
  geom_count() +
  scale_x_continuous(breaks = 260:266, labels = c("Gilgit", "Diamer", "Skardu", "Ghanshe", "Astore", "Ghizer", "Hunza-Nagar"))
    
```
<p>Within Gilgit-Baltistan, Hunza is outperforming.</p>


#### Basic Learning Levels: Reading in Local/National Language (C010)
1 = Begginer/Nothing; 2 = Letters; 3 = Words; 4 = Sentences; 5 = Story
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C010)) +
  geom_histogram()
```

```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(na = sum(is.na(C010)))
```

#### Basic Learning Levels by Age
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266, C013 != c(3,4)) %>% 
  ggplot(aes(C010)) +
  geom_histogram() +
  facet_grid(~C001)
# children at he age of 3 and 4 are removed for they have not data
```

#### Basic Learning Levels by Gender
```{r,message=FALSE, warning=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C010)) +
  geom_histogram() +
  facet_grid(~C002, labeller = labeller(C002 = Gender))
```

#### English Reading Levels (C013)
```{r, message=FALSE, warning=FALSE}
child %>% 
  filter(DID == 266, C013 != c(3,4)) %>% 
  ggplot(aes(C013)) +
  geom_histogram() +
  facet_grid(~C001)
# children at he age of 3 and 4 are removed for they have not data

```

#### English Reading Levels by Gender 
```{r, message=FALSE, warning=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C013)) +
  geom_histogram() +
  facet_grid(~C002, labeller = labeller(C002 = Gender))
```



### Comparison between Other Region
#### Current Enrollment Rate
```{r, message=FALSE}
child %>% 
  group_by(DID) %>% 
  mutate(avg = round(mean(C003 == 3), digits = 2)) %>% 
  ungroup() %>% 
  ggplot(aes(avg)) +
  geom_histogram() +
  facet_grid(~RID, labeller = labeller(RID = RegionName)) +
  labs(title = "Current Enrollment Rate by Region")
```

#### Female Average Learning Levels (Age or other variables are NOT adjusted)
```{r}
child %>% 
  filter(C002 == -1) %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_learning, color = RID)) +
  geom_point() +
  geom_text(aes(label = DID), nudge_x = 5, check_overlap = TRUE)

```
```{r}
child %>% 
  filter(C002 == -1) %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_learning, color = RID)) +
  geom_point() +
  geom_text(aes(label = DID), nudge_x = 5, check_overlap = TRUE) +
  gghighlight(RID == 6)
  
```
<p>It is interesting to note that Gilgit-Baltistan(RID==6) has a huge diversity in average learning levels of girls and Hunza(DID==266) is in the top group of all region.</p>


### Spatial Analysis
#### Districts Map
```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica <- sf::st_read("map/pak_ica_categories_areas_geonode_apr2017.shp")

ica %>% 
  mutate(
    centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(aes(x, y))
```
```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(aes(x, y)) +
  geom_text(aes(x, y, label = Districts),size = 2, check_overlap = TRUE, nudge_y = 1)
```


```{r}
ica_df <- ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
  as.data.frame()

ica_df <- ica_df %>% select(Province, Districts, x, y)
ica_df <- ica_df %>% summarize(Province = tolower(Province), Districts = tolower(Districts), x = x, y = y)


```

#### Child and ProvDist data combination

```{r}
child_dname <- child %>% left_join(provdist[-1])
child_dname <- child_dname %>% mutate(dname = tolower(DNAME))
```


```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_2 <- ica_df %>% filter(Province == "punjab")
ica_df_2$Districts <- ica_df_2$Districts %>%  
  str_replace("bahawalnagar", "bahawalnager") %>%
  str_replace("jhelum", "Jehlum") %>% 
  str_replace("leiah", "layyah") %>% 
  str_replace("mandi bahauddin", "mandi bahuddin") %>% 
  as.vector()


child_dname_2 <- child_dname %>% filter(RNAME == "Punjab") %>% left_join(ica_df_2, by = c("dname" = "Districts"))

child_dname_2 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_2
```
```{r}
ica_df_3 <- ica_df %>% filter(Province == "sindh")

ica_df_3$Districts <- ica_df_3$Districts %>%  
  str_replace("ghotki", "gotki") %>%
  str_replace("mirpur khas", "mirpurkhas") %>% 
  str_replace("malir karachi", "karachi-malir-rural") %>% 
  str_replace("naushahro feroze", "nowshero feroze") %>% 
  str_replace("kambar shahdad kot", "qambar shahdadkot") %>% 
  str_replace("sujawal", "sajawal") %>% 
  str_replace("shaheed benazir abad", "shaheed benazirabad") %>% 
  str_replace("tando allahyar", "tando allah yar") %>% 
  as.vector()

child_dname_3 <- child_dname %>% filter(RNAME == "Sindh") %>% left_join(ica_df_3, by = c("dname" = "Districts"))

child_dname_3 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_3
```
```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_4 <- ica_df %>% filter(Province == "balochistan")

ica_df_4$Districts <- ica_df_4$Districts %>%  
  str_replace("chagai", "chaghi") %>%
  str_replace("jaffarabad", "jafarabad") %>% 
  str_replace("kalat", "kallat") %>% 
  str_replace("kech", "kech (turbat)") %>% 
  str_replace("killa abdullah", "qilla abdullah") %>% 
  str_replace("killa saifullah", "qilla saifullah") %>% 
  as.vector()

child_dname_4 <- child_dname %>% filter(RNAME == "Balochistan") %>% left_join(ica_df_4, by = c("dname" = "Districts"))

child_dname_4 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_4
```



```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_5 <- ica_df %>% filter(Province == "khyber pakhtunkhwa")
ica_df_5

ica_df_5$Districts <- ica_df_5$Districts %>%  
  str_replace("batagram", "battagram") %>%
  str_replace("d. i. khan", "dera ismail khan") %>% 
  str_replace("malakand p area", "malakand") %>% 
  as.vector()

child_dname_5 <- child_dname %>% filter(RNAME == "Khyber Pakhtunkhwa") %>% left_join(ica_df_5, by = c("dname" = "Districts"))

child_dname_5 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_5

```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_6 <- ica_df %>% filter(Province == "gilgit baltistan")

ica_df_6$Districts <- ica_df_6$Districts %>%  
  str_replace("diamir", "diamer") %>%
  str_replace("hunza", "hunza-nagar") %>% 
  as.vector()

child_dname_6 <- child_dname %>% filter(RNAME == "Gilgit-Baltistan") %>% left_join(ica_df_6, by = c("dname" = "Districts"))

child_dname_6 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_6
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_7 <- ica_df %>% filter(Province == "azad kashmir")

ica_df_7$Districts <- ica_df_7$Districts %>%  
  str_replace("hattian bala", "hattian") %>%
  str_replace("haveli\\(kahuta\\)", "haveli") %>% 
  str_replace("sudhnoti", "sudhnati") %>% 
  as.vector()

child_dname_7 <- child_dname %>% filter(RNAME == "Azad Jammu and Kashmir") %>% left_join(ica_df_7, by = c("dname" = "Districts"))

child_dname_7 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_7
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_8 <- ica_df %>% filter(Province == "islamabad")
child_dname_8 <- child_dname %>% filter(RNAME == "Islamabad - ICT") %>% left_join(ica_df_8, by = c("dname" = "Districts"))

child_dname_8 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_8
```

```{r,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df_9 <- ica_df %>% filter(Province == "fata")

ica_df_9$Districts <- ica_df_9$Districts %>%  
  str_replace("fr bannu", "f.r. - bannu") %>%
  str_replace("fr d.i.khan", "f.r. - d.i. khan") %>% 
  str_replace("fr kohat", "f.r. - kohat") %>% 
  str_replace("fr lakki marwat", "f.r. - lakki marwat") %>% 
  str_replace("fr peshawar", "f.r. - peshawar") %>% 
  str_replace("fr tank", "f.r. - tank") %>% 
  as.vector()

child_dname_9 <- child_dname %>% filter(RNAME == "Federally Administrated Tribal Areas") %>% left_join(ica_df_9, by = c("dname" = "Districts"))

child_dname_9 %>% group_by(dname) %>% summarize(n = sum(x))
ica_df_9
```
```{r ica_df whose Districts names are renamed,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
ica_df
rbind(ica_df_2, ica_df_3, ica_df_4,
      ica_df_5, ica_df_6, ica_df_7,
      ica_df_8, ica_df_9)
```

```{r data child which as location,include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
child_ica <- rbind(child_dname_2, child_dname_3, child_dname_4,
      child_dname_5, child_dname_6, child_dname_7,
      child_dname_8, child_dname_9)
```

#### District IDs

```{r}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica, aes(x, y, label = DID, color = factor(RID))) +
  geom_text(data = child_ica, aes(x, y, label = DID), size = 5, nudge_y = 0.2, check_overlap = TRUE)
```

#### Gilgit-Baltistan Region

```{r}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica, aes(x, y, label = DNAME, shape = factor(RID), color = factor(RID))) +
  geom_text(data = child_ica, aes(x, y, label = DNAME), size = 4.5, nudge_y = 0.2, check_overlap = TRUE) +
  scale_shape_manual(values = 0:8) +
  coord_sf(xlim = c(71, 77.9), ylim = c(34, 37.1))
```

#### Latitudes and longitudes of Gilgit-Baltistan region

```{r}
child_ica %>% 
  filter(RID == 6) %>% 
  summarise(xmin = min(x), xmax = max(x), ymin = min(y), ymax = max(y))
```


#### Average enrollment rate

```{r, message=FALSE, warning=FALSE, error=FALSE, comment=FALSE}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica %>% group_by(DID) %>% 
               mutate(avg_enroll = mean(C003 == 3)), 
             aes(x, y, label = avg_enroll, color = avg_enroll))
  # geom_text(data = child_ica%>% group_by(DID) %>% 
  #             mutate(avg_enroll = mean(C003 == 3)), 
  #           aes(x, y, avg_enroll), check_overlap = TRUE, nudge_y = 0.5)
```

#### Average enrollment rate of female children

```{r}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica %>% filter(C002 == -1) %>% group_by(DID) %>% 
               mutate(avg_enroll = mean(C003 == 3)), 
             aes(x, y, label = avg_enroll, color = avg_enroll))
```



```{r, warning=FALSE, error=FALSE, comment=FALSE}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica, aes(x, y, label = C010, color = C010))
  # geom_text(data = child_ica, aes(x, y, label = C010), check_overlap = TRUE, nudge_y = 1)
```

#### Traial: children, gender
```{r, warning=FALSE, error=FALSE, comment=FALSE}
ica %>% 
  mutate(centroid = st_centroid(geometry),
    x = st_coordinates(centroid)[,1],
    y = st_coordinates(centroid)[,2]) %>% 
    ggplot() +
  geom_sf() +
  geom_point(data = child_ica %>% 
               group_by(DID) %>%
               mutate(gender_ratio = mean(C002)), 
             aes(x, y, label = gender_ratio, color = gender_ratio))
```
<div><p>0: male, -1: female</p></div><p>Thus, -0.5 indicates the complete gender parity</p>





### Children

#### Average Local/National Language Level Across Ages by Rgion
```{r, warning=FALSE, error=FALSE, comment=FALSE}
child_ica %>% 
  filter(C002 == c(0,-1)) %>% 
  group_by(DID, C001, C002) %>% 
  mutate(avg_local = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_local, color = factor(C002), group = DID)) +
  geom_line(show.legend = FALSE) +
  labs(x = "Age") +
  facet_grid(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  facet_wrap(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender))

```

#### Average Enrollment Rate

##### Across Ages by Rgion
```{r, warning=FALSE, error=FALSE, comment=FALSE}
child_ica %>% 
  filter(C002 == c(0,-1)) %>% 
  group_by(DID, C001, C002) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, color = factor(DID), group = DID)) +
  geom_line(show.legend = FALSE) +
  labs(x = "Age") +
  facet_grid(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  facet_wrap(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender))


```

##### Hunza
```{r, warning=FALSE, error=FALSE, comment=FALSE}
child_ica %>% 
  filter(C002 != "NA", RID == 6, RID != "NA") %>% 
  group_by(DID, C001, C002) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, color = factor(DID), group = DID)) +
  geom_line() +
  labs(x = "Age") +
  facet_grid(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  facet_wrap(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  gghighlight(label_key = DNAME, calculate_per_facet = TRUE)
```

```{r}
child_ica %>% 
  filter(C002 != "NA", RID == 6, RID != "NA") %>% 
  group_by(DID, C001, C002) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, color = factor(DID), group = DID)) +
  geom_line() +
  labs(x = "Age") +
  facet_grid(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  facet_wrap(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  gghighlight(DID == 266,label_key = DNAME, calculate_per_facet = TRUE)

```

##### Karachi 
```{r, warning=FALSE, error=FALSE, comment=FALSE}

child_ica %>% 
  filter(C002 != "NA", RID == 3) %>% 
  group_by(DID, C001, C002) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, color = factor(DID), group = DID)) +
  geom_line() +
  labs(x = "Age") +
  facet_grid(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  facet_wrap(RID~C002, labeller = labeller(RID = RegionName, C002 = Gender)) +
  gghighlight(DID == c(315,316), label_key = DNAME, calculate_per_facet = TRUE)
```

##### children Education Stage

```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", C010 != "NA", C002 != "NA") %>% 
  group_by(C005) %>% 
  summarize(n = n()) %>%
  mutate(C005 = fct_reorder(C005, n)) %>% 
  ggplot(aes(C005, n)) +
  geom_col() +
  coord_flip()
```




##### Hunza. Children Education Stage

```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", !is.na(C010), C002 != "NA", !is.na(C005), DID == 266) %>% 
  group_by(C005) %>% 
  summarize(n = n()) %>%
  mutate(C005 = fct_reorder(C005, n)) %>% 
  ggplot(aes(C005, n)) +
  geom_col() +
  coord_flip()
  
```

##### Enrollment and Gender within Gilgit-Baltistan

```{r}
child_ica %>% 
  filter(!is.na(C002), RID == 6) %>% 
  group_by(DID, C001, C002) %>% 
  mutate(enroll = mean(C003 == 3)) %>% 
  ggplot(aes(C001, enroll, group = C002, color = factor(C002))) +
  geom_line() +
  facet_wrap(.~DID)
```

##### Education Etages

```{r}
child_ica %>% 
  group_by(DID) %>% 
  mutate(n = length(C003),
            dropout = sum(C003 == 2),
            dropout_ratio = mean(C003 == 2),
            never = sum(C003 == 1),
            never_ratio = mean(C003 == 1)) %>% 
  ggplot(aes(DID, never_ratio, color = factor(RID))) +
  geom_point()
```


#### Child & Parents

##### Mother Enrollment by District

```{r}
child_ica %>%
  filter(RID == 6, PR004 != "NA") %>% 
  group_by(DID, PR004) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_enrollment, fill = factor(PR004))) +
  geom_col(aes(factor(DID), avg_enrollment, fill = factor(PR004)), position = "dodge")
```
<div><p>Within Gilgit-Baltistan, Hunza is the only district where there are more women who have experience of education than those who have never enrolled in schools.</p></div>

##### Father Enrollment by District

```{r}
child_ica %>%
  filter(RID == 6, PR009 != "NA") %>% 
  group_by(DID, PR009) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_enrollment, group = PR009, fill = factor(PR009))) +
  geom_col(aes(factor(DID), avg_enrollment), position = "dodge")
```

##### Mother's Education and Children Learning Level by Region. boxplot

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3)) %>% 
  ggplot(aes(PR004, avg_learning, group = PR004)) +
  geom_boxplot(aes(PR004, avg_learning)) +
  facet_grid(.~RID)

```

##### Father's Education and Children Learning Level by Region. boxplot

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3)) %>% 
  ggplot(aes(PR009, avg_learning, group = PR009)) +
  geom_boxplot(aes(PR009, avg_learning)) +
  facet_grid(.~RID)
```

##### Mother's Education and Children Learning Level by District

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3, na.rm = TRUE), mother_enrollment = mean(PR004, na.rm = TRUE)) %>% 
  ggplot(aes(mother_enrollment, avg_learning)) +
  geom_point()
```

 
```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3, na.rm = TRUE), mother_enrollment = mean(PR004, na.rm = TRUE)) %>% 
  ungroup() %>% 
  summarize(r = cor(mother_enrollment, avg_learning))
```

##### Father's Education and Children Learning Level by District

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3, na.rm = TRUE), father_enrollment = mean(PR009, na.rm = TRUE)) %>% 
  ggplot(aes(father_enrollment, avg_learning)) +
  geom_point()
```


```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA") %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C003 == 3), father_enrollment = mean(PR009)) %>% 
  ungroup() %>% 
  summarize(r = cor(father_enrollment, avg_learning))
```

##### Hunza. Age, Learning Level, Mother's Education, 

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA", C003 != "NA", DID == 266, C001 != "NA") %>% 
  group_by(PR004, C001) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_learning, group = PR004, color = factor(PR004))) +
  geom_line(aes(C001, avg_learning))
```

##### Hunza. Age, Learning Level, Father's Education

```{r}
child_ica %>% 
  filter(PR009 != "NA", PR004 != "NA", C003 != "NA", DID == 266, C001 != "NA") %>% 
  group_by(PR009, C001) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_learning, group = PR009, color = factor(PR009))) +
  geom_line(aes(C001, avg_learning))
```

##### Gilgit-Baltistan. Age, Learning Level, Mother's Education

```{r}
child_ica %>% 
  filter(PR009 != "NA", 
         PR004 != "NA", 
         C003 != "NA", 
         C001 != "NA",
         RID == 6) %>% 
  group_by(DID, PR004, C001) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_learning, group = PR004, color = factor(PR004))) +
  geom_line(aes(C001, avg_learning)) +
  facet_grid(.~DID) +
  facet_wrap(.~DID)
```

##### Gilgit-Baltistan. Age, Learning Level, Father's Education

```{r}
child_ica %>% 
  filter(PR009 != "NA", 
         PR004 != "NA", 
         C003 != "NA", 
         C001 != "NA",
         RID == 6) %>% 
  group_by(DID, PR009, C001) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_learning, group = PR009, color = factor(PR009))) +
  geom_line(aes(C001, avg_learning)) +
  facet_grid(.~DID) +
  facet_wrap(.~DID)
```

##### Gilgit-Baltistan. Age, Enrollment, Mother's Education

```{r}
child_ica %>% 
  filter(PR009 != "NA", 
         PR004 != "NA", 
         C003 != "NA", 
         C001 != "NA",
         RID == 6) %>% 
  group_by(DID, PR004, C001) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, group = PR004, color = factor(PR004))) +
  geom_line(aes(C001, avg_enrollment)) +
  facet_grid(.~DID) +
  facet_wrap(.~DID)
```

##### Gilgit-Baltistan. age, enrollment, father's education

```{r}
child_ica %>%
  filter(PR009 != "NA", 
         PR004 != "NA", 
         C003 != "NA", 
         C001 != "NA",
         RID == 6) %>% 
  group_by(DID, PR009, C001) %>% 
  mutate(avg_enrollment = mean(C003 == 3, na.rm = TRUE)) %>% 
  ggplot(aes(C001, avg_enrollment, group = PR009, color = factor(PR009))) +
  geom_line(aes(C001, avg_enrollment)) +
  facet_grid(.~DID) +
  facet_wrap(.~DID)
```

##### mothers education level

```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", C010 != "NA", C002 != "NA") %>% 
  ggplot(aes(PR005)) +
  geom_histogram(stat = "count") +
  coord_flip()
```

###### summary

```{r}
child_ica %>% 
  ggplot(aes(PR006)) +
  geom_histogram(stat = "count") +
  coord_flip()
```

##### fathers education level

```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", C010 != "NA", C002 != "NA") %>%
  ggplot(aes(PR010)) +
  geom_histogram(stat = "count") +
  coord_flip()
```
###### summary
```{r}
child_ica %>% 
  ggplot(aes(PR011)) +
  geom_histogram(stat = "count") +
  coord_flip()
```


##### mothers education level by region

```{r}
child_ica %>%
  group_by(DID, PR006) %>% 
  ggplot(aes(PR006)) +
  geom_histogram(aes(PR006), stat = "count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5)) +
  facet_grid(.~RID)
  
```


##### Mother enrollment by district


```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", C010 != "NA") %>% 
  group_by(DID) %>% 
  mutate(mother_edu_rate = sum(PR004 == -1)/length(PR004)) %>% 
  ggplot(aes(DID, mother_edu_rate, shape = factor(RID), color = factor(RID))) +
  geom_point() +
  scale_shape_manual(values = 0:8)
```

##### Gilgit-Baltistan. Average mother education experience, House type

```{r}
child_ica %>% 
  filter(PR004 != "NA", PR009 != "NA", C010 != "NA") %>% 
  group_by(DID) %>% 
  mutate(mother_edu_rate = sum(PR004 == -1)/length(PR004)) %>% ungroup() %>% 
  ggplot(aes(factor(RID), mother_edu_rate, group = RID)) +
  geom_violin()
```

##### Hunza. father enroll ratio

```{r}
child_ica %>% 
  filter(DID == 266, !is.na(PR009)) %>% 
  summarize(father_edu_ratio = sum(PR009 == -1)/length(PR009))
```

##### father enroll ratio

```{r}
child_ica %>% 
  filter(!is.na(PR009)) %>% 
  summarize(father_edu_ratio = sum(PR009 == -1)/length(PR009))
```

##### father enroll ratio by district

```{r}
child_ica %>% 
  filter(!is.na(PR009)) %>% 
  group_by(DID) %>% 
  mutate(father_edu_ratio = sum(PR009 == -1)/length(PR009)) %>% 
  ggplot(aes(factor(DID), father_edu_ratio)) +
  geom_point()
```

##### mother enroll ratio by district

```{r}
child_ica %>% 
  filter(!is.na(PR009), !is.na(PR004)) %>% 
  group_by(DID) %>% 
  mutate(mother_edu_ratio = sum(PR004 == -1)/length(PR004)) %>% 
  ggplot(aes(factor(DID), mother_edu_ratio)) +
  geom_point()
```








#### Child, Household

##### Number of Children in a household

```{r}
child_ica %>%
  filter(!is.na(PR004), !is.na(PR009)) %>% 
  filter(HHID == 96546) %>% 
  select(CID, PRID, C002, C001, PR001, VID, C003, DID, RID)

child_ica %>% 
  group_by(HHID) %>%
  mutate(n = n()) %>% 
  ggplot(aes(factor(n), fill = factor(RID))) +
  geom_bar(position = "dodge") +
  facet_grid(.~RID) +
  facet_wrap(.~RID)
```

##### house type ratio by region

```{r}
child_ica %>% 
  ggplot(aes(x = factor(DID), y = factor(H002), fill = factor(H002))) +
  geom_bar(aes(x = factor(DID), y = factor(H002)), stat = "identity", position = "fill") +
  facet_grid(.~RID, scales = "free") +
  facet_wrap(.~RID, scales = "free") +
  theme(axis.text.x = element_text(angle = 90, size = 7, hjust = 1)) +
  coord_cartesian(ylim = c(0,1), clip = "off", expand = FALSE)

```

##### Gilgit-Baltistan. house type

```{r}
child_ica %>% 
  filter(C003 != "NA", RID == 6) %>% 
  group_by(DID, H002) %>% 
  mutate(avg_enrollment = mean(C003 == 3)) %>% 
  ggplot(aes(factor(DID), avg_enrollment, group = H002, fill = factor(H002))) +
  geom_col(position = "dodge")
```

##### Hunza. house type

```{r}
child_ica %>% left_join(house, by = "HHID") %>% 
  filter(DID.x == 266) %>% 
  ggplot(aes(H002.x)) +
  geom_histogram(aes(H002.x), stat = "count")
```







#### Average Number of Children in a household

```{r}
child_ica %>% 
  group_by(HHID) %>% 
  mutate(n_children = length(unique(CID))) %>% 
  ungroup() %>% 
  group_by(DID) %>% 
  mutate(avg_n_children = mean(n_children)) %>% 
  ggplot(aes(DID, avg_n_children, color = factor(RID))) +
  geom_point()
```


```{r}
child_ica %>% 
  ggplot(aes(C005)) +
  geom_histogram(stat = "count") +
  coord_flip()
```


##### Hunza, house type

```{r}
child_ica %>% 
  filter(DID == 266) %>% 
  group_by(H002) %>% 
  summarize(n = n()) %>% 
  ggplot(aes(H002, n)) +
  geom_col() +
  geom_text(aes(label = n), vjust = 1.5, color = "white") +
  xlab("House Type") +
  ylab("Number of Households")
```

##### Hunza, number of children in households 

```{r}
child_ica%>% 
  filter(DID == 266) %>% 
  group_by(HHID) %>%
  summarize(n = length(unique(CID))) %>% 
  ungroup() %>% 
  group_by(n) %>% 
  summarize(num = n()) %>% 
  ggplot(aes(factor(n), num)) +
  geom_col() +
  geom_text(aes(label = num), vjust = -0.5) +
  xlab("Number of Children in Each Household") +
  ylab("Number of Households") 
  
```


#### Paid-Tuition 

```{r}
child_ica %>% 
  filter(PR009 == 0, !is.na(C008a)) %>% 
  summarize(n = length(unique(CID)),
            paid_tuition = sum(C008a == -1), 
            ratio = paid_tuition/n)
```

##### Hunza

```{r}
child_ica %>% 
  filter(DID == 266, PR009 == 0, !is.na(C008a)) %>% 
  summarize(n = length(unique(CID)),
            paid_tuition = sum(C008a == -1), 
            ratio = paid_tuition/n)
```


```{r}
child_ica %>% 
  filter(DID == 266, PR004 == 0, !is.na(C008a)) %>% 
  summarize(n = length(unique(CID)),
            paid_tuition = sum(C008a == -1), 
            ratio = paid_tuition/n)
```


##### paid tuition by district

```{r}
child_ica %>% 
  group_by(DID) %>% 
  mutate(avg_paid = mean(C008a == -1, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_paid)) +
  geom_point()+
  scale_y_continuous(limits = c(0,1))
```

```{r}
child_ica %>% 
  filter(!is.na(C002)) %>%
  group_by(DID) %>% 
  summarize(avg_paid = mean(C008a == -1),
         female = mean(child_ica %>% filter(C002 == -1) %>% 
                         group_by(DID) %>% .$C003 == 3),
         male = mean(child_ica %>% filter(C002 == 0) %>% 
                       group_by(DID) %>% .$C003 == 3),
         ratio = female/male)

```
```{r}
child_ica %>% 
  filter(!is.na(C002)) %>%
  group_by(DID, C002) %>% 
  summarize(enroll = mean(C003 == 3)) %>% 
  ungroup() %>% 
  spread(C002, enroll) %>% 
  summarize(DID = DID,
            gender_ratio = .$"-1"/.$"0") %>% 
  ggplot(aes(DID, gender_ratio)) +
  geom_point() +
  scale_y_continuous(limits = c(0,1))
```

##### correlation b/w paid-tuition and enrollment?

```{r}
child_ica %>% 
  filter(!is.na(C002)) %>%
  group_by(DID) %>% 
  mutate(paid_tuition = mean(C008a == -1, na.rm = TRUE)) %>% 
  group_by(DID, C002) %>% 
  mutate(enroll = mean(C003 == 3)) %>% 
  ggplot(aes(paid_tuition, enroll)) +
  geom_point() +
  geom_smooth() +
  facet_grid(.~C002)
  
```

#### VID

##### Gilgit (DID == 260)
```{r}
child_ica %>%
  filter(!is.na(C002), DID == 260) %>% 
  group_by(VID, C002) %>% 
  summarize(avg_enroll = mean(C003 == 3)) %>% 
  ggplot(aes(VID, avg_enroll, color = factor(C002))) +
  geom_point()
```



### Preparation for Logistic Regression Analysis

#### Making Dataframe With Dummy Variables


```{r}
child_ica_dummy <- child_ica %>% filter(!is.na(C002), !is.na(C003), !is.na(PR004), !is.na(PR009))
child_ica_dummy$C002_01 <- ifelse(child_ica_dummy$C002 == -1, 1, 0)
child_ica_dummy$C003_01 <- ifelse(child_ica_dummy$C003 == 3, 1, 0)
child_ica_dummy$PR004_01 <- ifelse(child_ica_dummy$PR004 == -1, 1, 0)
child_ica_dummy$PR009_01 <- ifelse(child_ica_dummy$PR009 == -1, 1, 0)
child_ica_dummy$PR004_PR009_01 <- ifelse(child_ica_dummy$PR004 == -1 | child_ica_dummy$PR009 == -1, 1, 0)
```

```{r}
n_children_in_household <- child_ica_dummy %>% 
  group_by(HHID) %>% 
  summarize(n_children_in_household = length(unique(CID)))

child_ica_dummy <- child_ica_dummy %>% left_join(n_children_in_household)

child_ica_dummy$H002_1_01 <- ifelse(child_ica_dummy$H002 == 1, 1, 0)
child_ica_dummy$H002_2_01 <- ifelse(child_ica_dummy$H002 == 2, 1, 0)
child_ica_dummy$H002_3_01 <- ifelse(child_ica_dummy$H002 == 3, 1, 0)
```

#### Create dummy variable with regard to region

```{r}
child_ica_dummy <- child_ica_dummy
child_ica_dummy$Panjab <- ifelse(child_ica_dummy$RID == 2, 1, 0)
child_ica_dummy$Sindh <- ifelse(child_ica_dummy$RID == 3, 1, 0)
child_ica_dummy$Balochistan <- ifelse(child_ica_dummy$RID == 4, 1, 0)
child_ica_dummy$Khyber_Pakhtunkhwa <- ifelse(child_ica_dummy$RID == 5, 1, 0)
child_ica_dummy$Gilgit_Baltistan <- ifelse(child_ica_dummy$RID == 6, 1, 0)
child_ica_dummy$Azad_Jammu_and_Kashmir <- ifelse(child_ica_dummy$RID == 7, 1, 0)
child_ica_dummy$Islamabad_ICT <- ifelse(child_ica_dummy$RID == 8, 1, 0)
child_ica_dummy$Federally_Administrated_Tribal_Areas <- ifelse(child_ica_dummy$RID == 9, 1, 0)
```


#### Eliminated NAs

```{r}
child_ica %>% 
  summarize(C002_na = sum(is.na(C002)),
            C003_na = sum(is.na(C003)),
            PR004_na = sum(is.na(PR004)),
            PR009_na = sum(is.na(PR009)))
```

#### Eliminated Rows in Total

```{r}
data.frame(original_rows = nrow(child_ica),
           eliminated_rows = nrow(child_ica) - nrow(child_ica_dummy),
           ratio = (nrow(child_ica)-nrow(child_ica_dummy))/nrow(child_ica))

```

#### Eliminated NAs Hunza

```{r}
child_ica %>% 
  filter(DID == 266) %>% 
  summarize(C002_na = sum(is.na(C002)),
            C003_na = sum(is.na(C003)),
            PR004_na = sum(is.na(PR004)),
            PR009_na = sum(is.na(PR009)))
```

#### Eliminated Rows in Total Hunza

```{r}
data.frame(original_rows = nrow(child_ica %>% filter(DID == 266)),
           eliminated_rows = nrow(child_ica %>% filter(DID == 266)) - nrow(child_ica_dummy %>% filter(DID == 266)),
           ratio = (nrow(child_ica %>% filter(DID == 266) %>% filter(DID == 266))-nrow(child_ica_dummy %>% filter(DID == 266)))/nrow(child_ica %>% filter(DID == 266)))

```





### Generalized Linear Models

#### GLM C003_01 ~ n_children_in_household + C002_01 + PR004_PR009_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + C002_01 + PR004_PR009_01, family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

#### Hunza. C003_01 ~ n_children_in_household + C002_01 + PR004_PR009_01

```{r}
glm_child_hunza <- glm(C003_01 ~ n_children_in_household + C002_01 + PR004_PR009_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))

ggPredict(glm_child_hunza, se = TRUE, show.summary = TRUE, point = TRUE, colorAsFactor = TRUE)
```
<div></div>

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child_hunza$y, y = fitted(glm_child_hunza))
```

##### exponential transformation

```{r}
exp(glm_child_hunza$coefficients)
```

##### confidence interval (intercept and coefficient)

```{r}
confint(glm_child_hunza, level = 0.95)
```

##### exponential transformation of confidence interval (odds ratio of intercept and coefficient)

```{r}
exp(confint(glm_child_hunza, level = 0.95))
```

##### AIC

```{r}
extractAIC(glm_child_hunza)
```

##### BIC

```{r}
extractAIC(glm_child_hunza, k = log(nrow(glm_child_hunza$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_hunza_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))
anova <- anova(glm_child_hunza_null, glm_child_hunza, test = "Chisq")
anova
```

##### variables selection

```{r}
step(glm_child_hunza_null, direction = "both", 
     scope = (~ C001 + C002_01 + PR004_01 + PR009_01))

```

##### multicolinearity

```{r}
vif(glm_child_hunza)
```







#### GLM C003_01 ~ n_children_in_household + H002 + PR004_PR009_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + H002 + PR004_PR009_01, family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

#### Hunza. C003_01 ~ n_children_in_household + H002 + PR004_PR009_01

```{r}
glm_child_hunza <- glm(C003_01 ~ n_children_in_household + H002 + PR004_PR009_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))

ggPredict(glm_child_hunza, se = TRUE, show.summary = TRUE, point = TRUE, colorAsFactor = TRUE)
```
<div></div>

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child_hunza$y, y = fitted(glm_child_hunza))
```

##### exponential transformation

```{r}
exp(glm_child_hunza$coefficients)
```

##### confidence interval (intercept and coefficient)

```{r}
confint(glm_child_hunza, level = 0.95)
```

##### exponential transformation of confidence interval (odds ratio of intercept and coefficient)

```{r}
exp(confint(glm_child_hunza, level = 0.95))
```

##### AIC

```{r}
extractAIC(glm_child_hunza)
```

##### BIC

```{r}
extractAIC(glm_child_hunza, k = log(nrow(glm_child_hunza$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_hunza_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))
anova <- anova(glm_child_hunza_null, glm_child_hunza, test = "Chisq")
anova
```

##### variables selection

```{r}
step(glm_child_hunza_null, direction = "both", 
     scope = (~ C001 + C002_01 + PR004_01 + PR009_01))

# step(glm_child_null, direction = "both", 
#      scope = (~ C001 + C002 + PR004_01 + PR009_01 + 
#                 Panjab + Sindh + Balochistan + Khyber_Pakhtunkhwa + Gilgit_Baltistan + 
#                 Azad_Jammu_and_Kashmir + Islamabad_ICT))

```

##### multicolinearity

```{r}
vif(glm_child_hunza)
```









#### GLM C003_01 ~ n_children_in_household + PR004_PR009_01 + H002

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + H002, family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

#### Hunza. C003_01 ~ n_children_in_household + PR004_PR009_01 + H002

```{r}
glm_child_hunza <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + H002, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))

ggPredict(glm_child_hunza, se = TRUE, show.summary = TRUE, point = TRUE, colorAsFactor = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```


#### Multicolinearity house type and parent edu?

```{r}
child_ica_dummy %>% 
  group_by(H002) %>% 
  mutate(n_parents = length(PR004_PR009_01))%>% 
  ggplot(aes(H002, n_parents, fill = factor(PR004_PR009_01))) +
  geom_col(position = "stack") +
  xlab("Type of Houses") +
  ylab("Number of Parents") +
  labs(fill = "Parents Education\n(at least one of them, primary or more)")

```
<div>The more educated the parents are, the better house they are living in.</div>








#### GLM C003_01 ~ n_children_in_household + H002 + C002_01

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + H002 + C002_01, family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```



#### Hunza. C003_01 ~ n_children_in_household + H002 + C002_01

```{r}
glm_child_hunza <- glm(C003_01 ~ n_children_in_household + H002 + C002_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))

ggPredict(glm_child_hunza, se = TRUE, show.summary = TRUE, point = TRUE, colorAsFactor = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child_hunza$y, y = fitted(glm_child_hunza))
```
<div></div>



##### exponential transformation

```{r}
exp(glm_child_hunza$coefficients)
```

##### confidence interval (intercept and coefficient)

```{r}
confint(glm_child_hunza, level = 0.95)
```

##### exponential transformation of confidence interval (odds ratio of intercept and coefficient)

```{r}
exp(confint(glm_child_hunza, level = 0.95))
```

##### AIC

```{r}
extractAIC(glm_child_hunza)
```

##### BIC

```{r}
extractAIC(glm_child_hunza, k = log(nrow(glm_child_hunza$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_hunza_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))
anova <- anova(glm_child_hunza_null, glm_child_hunza, test = "Chisq")
anova
```

##### variables selection

```{r}
step(glm_child_hunza_null, direction = "both", 
     scope = (~ C001 + C002_01 + PR004_01 + PR009_01))

# step(glm_child_null, direction = "both", 
#      scope = (~ C001 + C002 + PR004_01 + PR009_01 + 
#                 Panjab + Sindh + Balochistan + Khyber_Pakhtunkhwa + Gilgit_Baltistan + 
#                 Azad_Jammu_and_Kashmir + Islamabad_ICT))

```

##### multicolinearity

```{r}
vif(glm_child_hunza)
```










#### GLM C003_01 ~ n_children_in_household + C002_01 + H002

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + C002_01 + H002, family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```



#### Hunza. C003_01 ~n_children_in_household + C002_01 + H002

```{r}
glm_child_hunza <- glm(C003_01 ~n_children_in_household + C002_01 + H002, family = "binomial", data = child_ica_dummy %>% filter(DID == 266))

ggPredict(glm_child_hunza, se = TRUE, show.summary = TRUE, point = TRUE, colorAsFactor = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child_hunza$y, y = fitted(glm_child_hunza))
```





#### C002_01 chi Districts in Gilgit-Baltistan

```{r}
child_ica_dummy %>% filter(RID == 6) %>% summarize(unique(DID))
sapply(260:266, function(dist){
  glm_child_dist <- glm(C003_01 ~ C002_01, family = "binomial", data = child_ica_dummy %>% filter(RID == 6, DID == dist))
  glm_child_dist_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy %>% filter(RID == 6, DID == dist))
anova <- anova(glm_child_dist_null, glm_child_dist, test = "Chisq")
data.frame(result = anova$`Pr(>Chi)`[2], DID = dist, chi_0.05 = anova$`Pr(>Chi)`[2] >= 0.05)
})
```

<div>Within Gilgit-Baltistan, 3 of 7 districts including Hunza has Chi > 0.05</div>



#### GLM C003_01 ~ C002_01 and Anova for All Districts

```{r Logistic Regression for All Districts}
DID_unique <- child_ica_dummy %>% summarize(unique(DID))
DID_unique <- as.matrix(DID_unique)
DID_unique <- as.numeric(DID_unique[,1])

dist_logist <- sapply(DID_unique, function(dist){
  
  glm_child_dist <- glm(C003_01 ~ C002_01, 
                        family = "binomial", 
                        data = child_ica_dummy %>% 
                          filter(DID == dist))
  
  glm_child_dist_null <- glm(C003_01~1, 
                             family = "binomial", 
                             data = child_ica_dummy %>% 
                               filter(DID == dist))

  anova <- anova(glm_child_dist_null, glm_child_dist, test = "Chisq")

data.frame(DID = dist, 
           chi = anova$`Pr(>Chi)`[2], 
           chi_largerThan_0.05 = anova$`Pr(>Chi)`[2] >= 0.05, 
           chi_largerThan_0.1 = anova$`Pr(>Chi)`[2] >= 0.1)
})

anova_dist <- as.data.frame(as.tibble(t(dist_logist)))
anova_dist$DID <- as.numeric(anova_dist$DID)
anova_dist$chi <- as.numeric(anova_dist$chi)
anova_dist$chi_largerThan_0.1 <- as.logical(anova_dist$chi_largerThan_0.1)
anova_dist$chi_largerThan_0.05 <- as.logical(anova_dist$chi_largerThan_0.05)
```

```{r}
anova_dist %>% 
  summarize(total_chi_largerThan_0.05 = sum(as.numeric(chi_largerThan_0.05)),
            ratio_0.05 = sum(as.numeric(chi_largerThan_0.05))/length(chi_largerThan_0.05), 
            total_chi_largerThan_0.1 = sum(as.numeric(chi_largerThan_0.1)),
            ratio_0.1 = sum(as.numeric(chi_largerThan_0.1))/length(chi_largerThan_0.1))
```

##### DIDs with chi >= 0.05

```{r}
anova_dist %>% 
  filter(chi_largerThan_0.05 == TRUE) %>% 
  select(-chi_largerThan_0.1)
```

##### DID chi > 0.05

```{r}
DID_chi_0.05 <- anova_dist %>% 
  filter(chi_largerThan_0.05 == TRUE) %>% 
  select(DID) %>% 
  pull()
DID_chi_0.05
```

##### DIDs with chi >= 0.1

```{r}
anova_dist %>% 
  filter(chi_largerThan_0.1 == TRUE) %>% 
  select(-chi_largerThan_0.05)
```

##### DID chi > 0.1

```{r}
DID_chi_0.1 <- anova_dist %>% 
  filter(chi_largerThan_0.1 == TRUE) %>% 
  select(DID) %>% 
  pull()
```



##### DID with C002 == -1, chi > 0.05

```{r}
child %>% 
  filter(C002 == -1) %>% 
  group_by(DID) %>% 
  mutate(avg_learning = mean(C010, na.rm = TRUE)) %>% 
  ggplot(aes(DID, avg_learning)) +
  geom_point(data = child %>% 
               filter(C002 == -1 & DID == DID_chi_0.05) %>% 
               group_by(DID) %>%
               mutate(avg_learning = mean(C010, na.rm = TRUE)), size = 4, color = "red") +
  geom_point(aes(color = RID)) +
  geom_text(aes(label = DID), nudge_x = 5, check_overlap = TRUE)
```

##### C001 & enroll ; DID chi > 0.1

```{r}
child %>% 
  filter(DID == DID_chi_0.1) %>%
  group_by(DID, C001) %>% 
  mutate(enroll = mean(C003 == 3)) %>% 
  ggplot(aes(C001, enroll)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(DID~.)
```









#### GLM C003_01 ~ n_children_in_household + H002 + C002_01 + as.factor(DID)

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + H002 + C002_01 + as.factor(DID), family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

#### GLM C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(DID)

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(DID), family = "binomial", data = child_ica_dummy)

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### exponential transformation

```{r}
exp(glm_child$coefficients)
```

##### confidence interval (intercept and coefficient)

```{r}
# confint(glm_child, level = 0.95)
```

##### exponential transformation of confidence interval (odds ratio of intercept and coefficient)

```{r}
# exp(confint(glm_child, level = 0.95))
```

##### AIC

```{r}
extractAIC(glm_child)
```

##### BIC

```{r}
extractAIC(glm_child, k = log(nrow(glm_child$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy)
anova(glm_child_null, glm_child, test = "Chisq")
```

##### variables selection

```{r}
# step(glm_child_null, direction = "both", 
#      scope = (~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(DID)))
```

##### multicolinearity

```{r}
vif(glm_child)

```


##### Districts with P-Values Bigger Than 0.05 and Coefficient

```{r}
glm_summary <- glm_child %>% summary()
glm_coef <- as.data.frame(glm_summary$coefficients)
glm_coef %>% filter(`Pr(>|z|)` > 0.05)
```

##### Districts with P-Values Bigger Than 0.05

```{r}
glm_coef %>% filter(`Pr(>|z|)` > 0.05) %>% t() %>% .[-c(1:5),]
```
```{r}
dists_not_fit <-  c(148, 151, 162, 163, 178, 181, 193, 249, 260, 265, 269, 270, 271, 272, 274, 276, 277)
child_ica_dummy %>% filter(DID == dists_not_fit) %>% select(DID, DNAME) %>% summarize(DID = unique(DID), DNAME = unique(DNAME))
```

##### Districts with P-Values Bigger Than 0.001 and Coefficient

```{r}
glm_summary <- glm_child %>% summary()
glm_coef <- as.data.frame(glm_summary$coefficients)
glm_coef %>% filter(`Pr(>|z|)` > 0.001)
```

##### Districts with P-Values Bigger Than 0.001

```{r}
glm_coef %>% filter(`Pr(>|z|)` > 0.001) %>% t() %>% .[-c(1:5),]
```
```{r}
dists_not_fit <-  c(148, 151, 152, 158, 162, 163, 173, 178, 181, 185, 193, 199, 232, 238, 245, 249, 256, 260, 265, 267, 269, 270, 271, 272, 273, 274, 276, 277)
child_ica_dummy %>% filter(DID == dists_not_fit) %>% select(DID, DNAME) %>% summarize(DID = unique(DID), DNAME = unique(DNAME))
```



#### Dists_not_fit. GLM C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01

##### All of dists_not_fit

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(VID), family = "binomial", data = child_ica_dummy %>% filter(DID %in% dists_not_fit))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```


##### 148

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 148))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### 151

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 151))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### 260

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01, family = "binomial", data = child_ica_dummy %>% filter(DID == 260))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```

##### 260, VID

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + factor(VID), family = "binomial", data = child_ica_dummy %>% filter(DID == 260))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```



#### Without dists_not_fit. GLM C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(DID)

```{r}
glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01 + as.factor(DID), family = "binomial", data = child_ica_dummy %>% filter(!DID %in% dists_not_fit))

ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)

```

##### Hosmer-Lemeshow

```{r}
hoslem.test(x = glm_child$y, y = fitted(glm_child))
```











#### fit the momdel for every districts using apply function

#### All Districts. C003_01 ~ n_children_in_household PR004_PR009_01 + C002_01

```{r}
fit_all <- sapply(DID_unique, function(id){
  
  glm_child <- glm(C003_01 ~ n_children_in_household + PR004_PR009_01 + C002_01, 
                   family = "binomial", data = child_ica_dummy %>% filter(DID == id))
  
  # ggPredict(glm_child, se = TRUE, colorAsFactor = TRUE, show.summary = TRUE, point = TRUE)
  
  hoslem <- hoslem.test(x = glm_child$y, y = fitted(glm_child))
  data.frame(id, hoslem["p.value"])
}) %>% t()

fit_all <- fit_all %>% as.data.frame()

fit_all$id <- fit_all$id %>% as.numeric()
fit_all$p.value <- fit_all$p.value %>% as.numeric()

fit_all
```

##### Districts whose model is not fitted well

```{r}
fit_all %>% 
  filter(p.value < 0.05)
```



















### memo

#### fit the model

```{r}
glm_child <- glm(C003_01~ C001 + C002_01 + PR004_01, family = "binomial", data = child_ica_dummy)

summary(glm_child)
```

##### exponential transformation

```{r}
exp(glm_child$coefficients)
```

##### confidence interval (intercept and coefficient)

```{r}
confint(glm_child, level = 0.95)
```

##### exponential transformation of confidence interval (odds ratio of intercept and coefficient)

```{r}
exp(confint(glm_child, level = 0.95))
```

##### AIC

```{r}
extractAIC(glm_child)
```

##### BIC

```{r}
extractAIC(glm_child, k = log(nrow(glm_child$data)))
```

##### effectiveness of explanatory variables

```{r}
glm_child_null <- glm(C003_01~1, family = "binomial", data = child_ica_dummy)
anova(glm_child_null, glm_child, test = "Chisq")
```

##### variables selection

```{r}
step(glm_child_null, direction = "both", 
     scope = (~ C001 + C002_01 + PR004_01 + PR009_01))
```

##### multicolinearity

```{r}
vif(glm_child)

```










