---
title: "Exploring ASER2016 Pakistan Data"
author: "Yusei Hara"
date: "2020/10/1"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ASER Pakistan 2016

<p>In this piece of paper, a set of data obtained from Annual Status of Education Report (ASER) is explored. The raw data was downloaded from the link here. https://palnetwork.org/aser-centre/</p>

### Preparation
#### Packages Used
```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
```
#### Data Installation
```{r}
school <- read.csv("aser/ASER2016GSchool.csv")
child <- read.csv("aser/ASER2016Child.csv")
```
```{r}
RegionName <- c("2" = "Panjab", 
                "3" = "Sindh", 
                "4" = "Balochistan", 
                "5" = "Khyber Pakhtunkhwa", 
                "6" = "Gilgit-Baltistan", 
                "7" = "Azad Jammu and Kashmir", 
                "8" = "Islamabad - ICT", 
                "9" = "Federally Administrated Tribal Areas")
Gender <- c("0" = "Male",
            "-1" = "Female")
```

### Exploration
#### Checking Samplesizes
```{r}
length(unique(child$CID))
```
<p>The whole samplesize (the numebr of children) of this dataset is 255196.</p>
```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(N_hunza = length(unique(CID)))
```
<p>The samplesize of Hunza alone is 1641.</p>









### Exploration in Hunza
#### Gender Proportion
```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(gender_proportion = mean(C002))
```
<p>-1: female, 0: male<br>
gender_proportion = -0.5173675 means there are a little more girls in the dataset.</p>

#### Age of Children (C001)
```{r, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C001)) +
  geom_histogram()
```
Age is well sparsed

#### Eduation Status

```{r}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C003)) +
  geom_histogram(bins = 3)
```
1 = never enrolled; 2 = drop-out; 3 = currently enrolled

#### Education Status by Gender
```{r}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C003)) +
  geom_histogram(bins = 3, binwidth = 1) +
  facet_grid(~C002, labeller = labeller(C002 = Gender))
```
Both genders look pretty good interms of the absolute number of currently-enrolled-children 

#### The Enrollment Rate by Gender
```{r, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  group_by(C002) %>% 
  summarize(enrollment_rate = mean(C003 == 3)) %>% 
  ungroup() %>% 
  ggplot(aes(C002, enrollment_rate)) +
  geom_col() +
  scale_y_continuous() +
  geom_label(aes(label = enrollment_rate)) +
  scale_x_continuous(breaks = c(-1, 0), labels = c("Female", "Male"))
```
As a rate, both are doing pretty good

#### Currently-Enrolled: Institution Type (C006)
1 = Government; 2 = Private; 3 = Madrasah(Conventional religious education) School; 4 = Other(Non formal education facility)
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C006)) +
  geom_histogram()
```

Most children go to public schools or private schools



#### Comparison between Other Region
```{r, message=FALSE}
child %>% 
  group_by(DID) %>% 
  mutate(avg = round(mean(C003 == 3), digits = 2)) %>% 
  ungroup() %>% 
  ggplot(aes(avg)) +
  geom_histogram() +
  facet_grid(~RID, labeller = labeller(RID = RegionName)) +
  labs(title = "Current Enrollment Rate by Region")

```

#### Within Gilgit-Baltistan 
```{r}
child %>% 
  filter(RID == 6) %>% 
  group_by(DID) %>% 
  mutate(Current_Enrollment_Rate = mean(C003 == 3)) %>% 
  ggplot(aes(DID, Current_Enrollment_Rate)) +
  geom_count() +
  scale_x_continuous(breaks = 260:266, labels = c("Gilgit", "Diamer", "Skardu", "Ghanshe", "Astore", "Ghizer", "Hunza-Nagar"))
    
```
Within Gilgit-Baltistan, Hunza is outperforming.


#### Basic Learning Levels: Reading in Local/National Language (C010)
1 = Begginer/Nothing; 2 = Letters; 3 = Words; 4 = Sentences; 5 = Story
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C010)) +
  geom_histogram()
```

```{r}
child %>% 
  filter(DID == 266) %>% 
  summarize(na = sum(is.na(C010)))
```

#### Basic Learning Levels by Age
```{r, warning=FALSE, message=FALSE}
child %>% 
  filter(DID == 266) %>% 
  ggplot(aes(C010)) +
  geom_histogram() +
  facet_grid(~C001)
```




